---
title: "RIA5TSA"
author: ""
date: "30 October 2018"
output: pdf_document
---

# Overview

Provide an overview of what the module does / how to use the module.

Module documentation should be written so that others can use your module.
This is a template for module documentation, and should be changed to reflect your module.

## R Markdown

R Markdown syntax allows R code, outputs, and figures to be rendered in the documentation.

For help writing in R Markdown, see http://rmarkdown.rstudio.com/.

# Usage

```{r module_usage}
library(SpaDES)
library(data.table)
library(raster)
library(LandR)

googledrive::drive_auth(email = 'ianmseddy@gmail.com')

setPaths(cachePath =  '/mnt/data/RIA/cache',
         modulePath = c("modules/", 'modules/scfm/modules'), #if running scfm, 
         inputPath = file.path("inputs"),
         outputPath = file.path("outputs/LandRCS_no1") # shows where the 4 relevant paths are
         )

getPaths()
times <- list(start = 2011, end = 2051) #run to 2101 eventually 

parameters <- list(
  Biomass_core = list(
    .plotInitialTime = 2011
    , seedingAlgorithm = "wardDispersal"
    , .plotInterval = 10
    , .useCache = "init"
    , successionTimestep = 10
    , initialBiomassSource = "cohortData"
    , sppEquivCol = "RIA"
    , growthAndMortalityDrivers = "LandR.CS"
    , vegLeadingProportion = 0
    , .saveInitialTime = 2021
    , .saveInterval = 10
    , plotOverstory = TRUE
    , .plotMaps = FALSE
    , .maxMemory = 10
    , .useParallel = NA
  ),
  scfmSpread =  list(
    .plotInitialTime = NA
    , .plotInterval = 1
  ),
  scfmLandcoverInit = list(
    .plotInitialTime = NA
  )
  , Biomass_regeneration = list(
    fireInitialTime = times$start + 1,
    fireTimestep = 1,
    successionTimestep = 10
  )
  , gmcsDataPrep = list(
    useHeight = TRUE,
    GCM = "CCSM4_RCP8.5",
    cacheClimateRas = FALSE
    )
  , LandR_speciesParameters = list(
    sppEquivCol = 'RIA'
    , useHeight = FALSE
    , GAMMknots = list(
      "Abie_las" = 3,
      "Betu_pap" = 3,
      "Pice_eng" = 4,
      "Pice_gla" = 4, #4 achieves a flat instead of downard-sloping curve
      "Pice_mar" = 4,
      "Pinu_con" = 4, 
      "Popu_tre" = 4
    ),
    quantileAgeSubset = list(
      "Abie_las" = 95, #N = 250 '' 
      "Betu_pap" = 95, #N = 96
      "Pice_eng" = 95, #N = 130
      "Pice_gla" = 95, #N = 1849
      "Pice_mar" = 95, #N = 785
      "Pinu_con" = 97, # N = 3172, 99 not an improvement. Maybe 97
      "Popu_tre" = 98 # N = 1997, trying 99
    )
  )
)

modules <- list("PSP_Clean",  "gmcsDataPrep", "LandR_speciesParameters", "Biomass_core", "Biomass_regeneration", 
               "scfmLandcoverInit", "scfmRegime", "scfmDriver", "scfmIgnition", "scfmEscape", "scfmSpread")

objectSynonyms <- list(c('vegMap', "LCC2005"))

rasterToMatch <- prepInputs(url = 'https://drive.google.com/open?id=1dl1iS3eXWcMcc7ASI8eIrKyn-x3OM_Cx',
                            destinationPath = paths$inputPath)

studyArea <- prepInputs(url = 'https://drive.google.com/open?id=18XPcOKeQdty102dYHizKH3ZPE187BiYi',
                        destinationPath = paths$inputPath, 
                        targetFile = "RIA_fiveTSA.shp",
                        fun = 'shapefile',
                        alsoExtract = 'similar')
studyAreaPSP <- prepInputs(url = 'https://drive.google.com/open?id=10yhleaumhwa3hAv_8o7TE15lyesgkDV_',
                           destinationPath = paths$inputPath,
                           targetFile = 'ecodistrictsRIA.shp',
                           fun = 'shapefile',
                           alsoExtract = 'similar') #this is the overlap (not intersection) of ecoregions around RIA
studyAreaLarge <- prepInputs(url = "https://drive.google.com/open?id=1FlC5YdjNF8wXLcA4hQxLvrRjVC6ShqND",
                             destinationPath = paths$inputPath,
                             fun = 'shapefile',
                             alsoExtract = 'similar') #this is the whole RIA in BC. 
#I don't know if SA large is used by any module other than Biomass_boreal and Biomass_speciesData


source('generateSppEquiv.R')
source('generateSpeciesLayersRIA5TSA.R') #this uses the larger study area 

objects <- list(
  # cloudFolderID = cloudFolderID,
  studyArea = studyArea,
  rasterToMatch = rasterToMatch,
  sppEquiv = sppEquivalencies_CA,
  sppColorVect = sppColors,
  studyAreaLarge = studyAreaLarge,
  studyAreaReporting = studyArea,
  studyAreaPSP = studyAreaPSP,
  objecSynonyms = objectSynonyms,
  biomassMap = simOutSpp$biomassMap,
  cohortData = simOutSpp$cohortData,
  ecoDistrict = simOutSpp$ecodistrict,
  ecoregion = simOutSpp$ecoregion,
  ecoregionMap = simOutSpp$ecoregionMap,
  pixelGroupMap = simOutSpp$pixelGroupMap,
  minRelativeB = simOutSpp$minRelativeB,
  species = simOutSpp$species,
  speciesEcoregion = simOutSpp$speciesEcoregion,
  sufficientLight = simOutSpp$sufficientLight,
  rawBiomassMap = simOutSpp$rawBiomassMap,
  speciesLayers = simOutSpp$speciesLayers
)
          
opts <- options(
  "LandR.assertions" = FALSE,
  "reproducible.futurePlan" = FALSE,
  "reproducible.inputPaths" = NULL,
  "reproducible.quick" = FALSE,
  "reproducible.overwrite" = TRUE,
  "reproducible.useMemoise" = FALSE, # Brings cached stuff to memory during the second run
  "reproducible.useNewDigestAlgorithm" = TRUE,  # use the new less strict hashing algo
  "reproducible.useCache" = TRUE,
  "reproducible.cachePath" = paths$cachePath,
  "spades.moduleCodeChecks" = FALSE, # Turn off all module's code checking
  "spades.useRequire" = FALSE # assuming all pkgs installed correctly
)


startTime <- Sys.time()
data.table::setDTthreads(2) #
set.seed(11111)
mySim <- simInit(times = times, params = parameters, modules = modules, objects = objects,
                 paths = paths, loadOrder = unlist(modules))
mySimOut <- spades(mySim, debug = TRUE)
```

```{r explorig elevation}



```


